HUME: Human UCCA-Based Evaluation of Machine Translation

### 2016-03-17 paper/main.tex
sss

HUME uses just one structural annotation (for the source) while HMEANT relies on
two independently constructed structural annotations (for both the reference and
the candidate translation).

We see this difference as crucial where semantic analysis is concerned, as it
is often impossible to assign a semantic structure to a low quality MT output sentence.

For instance, consider the sentence ``A coronary angioplasty may not be technically possible'',
which was translated by one of the systems we experimented with as
``Eine koronare Angioplastie kann nicht technisch m{\"o}glich'', i.e., the main verb ``sein'' (``be'') is omitted.
While this may be interpreted is a minor error, HMEANT will assign it a very low score, as it failed to
translate the main verb.

We understand that this is a design feature of HMEANT:
if the translation per se cannot be annotated with verbal argument structure
(for whatever reason, including incomprehensibility), it cannot convey the meaning.

HMEANT thus makes a stricter check of whether the translation can be understood
than we do. HUME may be artificially boosting the perceived understandability of
the sentence by providing the source.

>>>>

HUME uses just one structural annotation (for the source) while HMEANT relies on
two independently constructed structural annotations (for both the reference and
the candidate translation).
We see this difference as crucial where semantic analysis is concerned, as it
is often impossible to assign a semantic structure to a low quality MT output sentence.

A design principle of HMEANT states that
if the translation cannot be annotated with verbal argument structure
(for whatever reason, including incomprehensibility), it cannot convey the meaning,
while HUME does not share this theoretical commitment.
For instance, consider the sentence ``a coronary angioplasty may not be technically possible'',
and the translation ``eine koronare Angioplastie kann nicht technisch m{\"o}glich''
(lit. ``a coronary angioplasty can not technically possible''),
produced by an MT system in our experiments.
The translation is correct, except that the main verb ``sein'' (``be'') is omitted.
While this may be interpreted is a minor error, HMEANT will assign it a very low score,
as it failed to translate the main verb.

However, HMEANT's independent annotation of the source and translation makes a stricter check
of whether the translation can be understood.
than we do. HUME may be artificially boosting the perceived understandability of
the sentence by allowing access to the source.
